A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-19 sanity/paper1.tex
Final fixes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1104 43ef1190-90fd-4dd7-a769-d0121f02b80e

\rdfterm{dct:modified} occured in 2687 triples, but 2487 of these does
not have the Request-URI of the information resource as their subject,
i.e. it gives the last modification time of some subgraph of the
returned RDF. Nevertheless, given its prevalence, it is highly likely
that the presence of \rdfterm{dct:modified} will be useful in
determining a heuristic freshness lifetime, as the latest date may be
used.

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, Axel Polleres for encouraging comments
and Jonas Smedegaard for proofreading. We also thank the anonymous
reviewers for extensive reviews. Many to Helen Murray for linguistic
assistance.

>>>>

\rdfterm{dct:modified} occurred in 2687 triples, but 2487 of these does
not have the Request-URI of the information resource as their subject,
i.e. it gives the last modification time of some subgraph of the
returned RDF. Nevertheless, given its prevalence, it is highly likely
that the presence of \rdfterm{dct:modified} will be useful in
determining a heuristic freshness lifetime, as the latest date may be
used.

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, Axel Polleres for encouraging comments
and Jonas Smedegaard for proofreading. We also thank the anonymous
reviewers for extensive reviews. Finally, many thanks to Helen Murray
for linguistic assistance.
